Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-24 ms.tex
switch order of terms in dipole/quadrupole regression equations
address more comments in zero level discussion, define c_nu earlier

The need for additional low-order corrections beyond a simple scalar offset 
became evident upon inspecting the HFI maps at 100-545 GHz. In particular, we 
noticed the presence of a residual dipole pattern, with an orientation 
consistent with that of the Solar dipole. To most precisely recover the 
amplitude of the residual dipole, it is necessary to have the 
highest-possible S/N in the independent variable of our regression. For 
this reason we have used 857 GHz as a reference for the 100-545 GHz bands, as 
opposed to the FDS99 predictions or H\,\textsc{i}.

@@

\begin{equation} \label{equ:dip}
\mathcal{I}_{\nu_i, p} = m\mathcal{I}_{857, p} + d\mathcal{D}_{p} + b
\end{equation}

With $p$ denoting a single nside=64 HEALPix pixel in the maps 
$\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
resolution \PLANCK~HFI map with zodiacal emission and compact sources removed. 
In the context of Equation \ref{equ:dip}, $\nu_i \in$  
\{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in
the native units of the relevant \PLANCK~band. $\mathcal{D}$ is a scaling of 
the Solar dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit amplitude. Because 
$\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
overconstrained linear model with three parameters: $m$, $d$, and $b$. $m$ 
represents the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz 
assuming they are linearly related. $d$ gives the residual Solar dipole
amplitude, and its best-fit value represents the scaling of the Solar dipole 
that makes the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly 
linear. $b$ represents the constant offset that must be subtracted from the 
band $\nu_i$ map to make its zero level consistent with that of the 857 GHz 
map. For each band $\nu_i$, we obtain estimates of $m$, $d$, and $b$ by 
performing a linear least squares fit with uniform weights and iterative 
outlier rejection. Figure \ref{fig:dip} shows scatterplots of the band $\nu_i$ 
versus 857 GHz correlation before and after correcting for the best-fit offset 
and residual dipole, for each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only 
are the tightened correlations striking in these scatterplots, but the residual
dipole subtractions appear very successful in the two-dimensional band $\nu_i$ 
maps themselves. Before performing thermal dust fits, we therefore subtract the
best-fit $b$ and $d\mathcal{D}$ from each band $\nu_i$ map. The best-fit
offsets and residual dipole amplitudes are listed in Table \ref{table:offs}.

@@

\begin{equation} \label{equ:quad}
\mathcal{I}_{100, p} = m\mathcal{I}_{857, p} + d\mathcal{D}_p + b + qQ_p
\end{equation}

>>>>

The need for additional low-order corrections beyond a simple scalar offset 
became evident upon inspecting the HFI maps at 100-545 GHz. In particular, we 
noticed the presence of a residual dipole pattern, with an orientation 
consistent with that of the Solar dipole. To most precisely recover the 
amplitude of the residual dipole, it is necessary to have the highest available
S/N in the independent variable of our regression. For this reason we have used
857 GHz as a reference for the 100-545 GHz bands, as opposed to the FDS99 
predictions or H\,\textsc{i}.

@@

\begin{equation} \label{equ:dip}
\mathcal{I}_{\nu_i, p} = m\mathcal{I}_{857, p} + b + d\mathcal{D}_{p}
\end{equation}

With $p$ denoting a single nside=64 HEALPix pixel in the maps 
$\mathcal{I}_{857}$, $\mathcal{I}_{\nu_i}$, and $\mathcal{D}$. Here 
$\mathcal{I}_{857}$ is the \PLANCK~857 GHz map with zodiacal emission, compact 
sources, and the constant offset of $\S$\ref{sec:zp_abs} removed, smoothed to 
$1^{\circ}$ resolution. $\mathcal{I}_{\nu_i}$ is the corresponding $1^{\circ}$ 
resolution \PLANCK~HFI map with zodiacal emission and compact sources removed. 
In the context of Equation \ref{equ:dip}, $\nu_i \in$  
\{100, 143, 217, 353, 545\} GHz. Note that $\mathcal{I}_{\nu_i}$ is always in
the native units of the relevant \PLANCK~band. $\mathcal{D}$ is a scaling of 
the Solar dipole pattern oriented toward 
$(l, b) = (263.99^{\circ}, 48.26^{\circ})$, with unit amplitude. Because 
$\sim$18,000 pixels satisfy the low H\,\textsc{i} cut, we have an 
overconstrained linear model with three parameters: $m$, $d$, and $b$. $m$ 
represents the best-fit slope of \PLANCK~band $\nu_i$ versus \PLANCK~857 GHz 
assuming they are linearly related. $d$ gives the residual Solar dipole
amplitude, and its best-fit value represents the scaling of the Solar dipole 
that makes the \PLANCK~band $\nu_i$ versus 857 GHz correlation most tightly 
linear. $b$ represents the constant offset that must be subtracted from the 
band $\nu_i$ map to make its zero level consistent with that of the 857 GHz 
map. For each band $\nu_i$, we obtain estimates of $m$, $d$, and $b$ by 
performing a linear least squares fit with uniform weights and iterative 
outlier rejection. Figure \ref{fig:dip} shows scatterplots of the band $\nu_i$ 
versus 857 GHz correlation before and after correcting for the best-fit offset 
and residual dipole, for each $\nu_i \in$ \{143, 217, 353, 545\} GHz. Not only 
are the tightened correlations striking in these scatterplots, but the residual
dipole subtractions appear very successful in the two-dimensional band $\nu_i$ 
maps themselves. Before performing thermal dust fits, we therefore subtract the
best-fit $b$ and $d\mathcal{D}$ from each band $\nu_i$ map. The best-fit
offsets and residual dipole amplitudes are listed in Table \ref{table:offs},
along with other important per-band parameters, such as the fractional 
multiplicative calibration uncertainty $c_{\nu}$.

@@

\begin{equation} \label{equ:quad}
\mathcal{I}_{100, p} = m\mathcal{I}_{857, p} + b + d\mathcal{D}_p + qQ_p
\end{equation}
